Using cosmic variance to constrain the dark matter halo mass of Lyman-alpha emitting galaxies at $z$=3.1

### 2013-05-27 paper/ms.tex
finished whole Methodology section

In our model a dark matter halo can only host one or zero LAE. 
There are three parameters in the model that decide whether a halo can host a
galaxy or not: the lower and upper bouds for the mass range $M_{\rm min}<
M_{\rm halo} < M_{\rm max}$ where LAEs reside and the fraction $f_{\rm
  occ}$ of such halos that effectively host a LAE. We do not assign a
luminosity to each each LAE. We are primaraly interested in
constraining the halo mass range hosting detectable LAEs under the
conditions defined by \cite{Yamada2012}. In what follows will describe by
the letter ${\mathcal M}$ a model defined by an specific choice of the
three scalar parameters $M_{\rm min}$, $M_{\rm  max}$ y $f_{\rm occ}$.

For each model ${\mathcal M}$ we create a set of mock fields from
disjoint volumes in the simulation. Each volume has the same geometry
probed by Suprime-CAM and the narrow band filter, namely rectangular
cuboids of dimensions $46\times 35\times 41$ $h^{-3}$Mpc$^{3}$ where
the last dinemsion goes in the redshift direction. This corresponds to
a total area of $880$ arcmin$^{2}$ in each mock field. We construct a total
$5\times 7 \times 6=210$ of such volumes from a snapshot in the Bolshoi
simulation.

@@

\subsection{Model Sampling and Selection}

We generate a series of models ${\mathcal M}$ with different input
parameters$\{M_{\rm min}, M_{\rm max}, f_{\rm occ}\}$ as
follows. $M_{\rm min}$ and $M_{\rm max}$ are allowed to take 30
different values evenly spaced by $0.1$ dex, $M_{\rm min}$ ranges from
$\log_{10}M_{\rm min}=10.0$ up to $\log_{10}M_{\rm min}=12.9$, while
$M_{\rm max}$ range  from $\log_{10}M_{\rm min}=10.1$ up to
$\log_{10}M_{\rm min}=13.0$. The occupation fraction $f_{\rm occ}$
takes 100 different values from $0.01$ to $1.00$ regularly spaced by
$0.01$. In total the number of different sets of input parameters to
be explored is $30 \times 30\times 100 = 9\times 10^{4}$.

For each model ${\mathcal M}$ we compute the LAE surface density
distributions for the three different ways of grouping the mock
fields, as described in the previous section. For each sub-volume we
project the positions of the LAE hosting halos along the $z$ direction
and calculate its surface number density in units of sources per
arcmin$^{2}$. For each number density distribution we perform a
Kolmogorov-Smirnov against the $12$ surface density observational
values. From this test we obtain the value $0<P<1$ to reject the null
hypothesis, namely that the two data sets come from the same
distribution. In this paper we use values of $P>0.1$ to consider that
the simulated and observed number densities come from the same
distribution.

@@

\begin{figure}
\begin{center}
\includegraphics[width=1.00\linewidth,angle=0]{./plots/Fig1.pdf}
\caption{ \label{figure:laes_dist} Cumulative mass function of dark
  matter haloes in the $210$ sub-volumes of $46\times 35\times 41$
  $h^{-3}Mpc^{3}$. The variation in the total number of dark matter
  halos per sub-volume  evidences the effect of cosmic variance at
  such sub-volume scale. It is also appreciable the low population
  $\lesssim10^{-3}h^{2}Mpc^{-2}$ of halos with
  $log(M/M_{\odot})>12.0$}. 
\end{center} 
\end{figure}

@@

\subsection{Additional Constraints}

>>>>

In our model a dark matter halo can only host one or zero LAE. 
There are three parameters in the model that decide whether a halo can host a
galaxy or not: the lower and upper bouds for the mass range $M_{\rm min}<
M_{\rm h} < M_{\rm max}$ where LAEs reside and the fraction $f_{\rm
  occ}$ of such halos that effectively host a LAE. We do not assign a
luminosity to each each LAE. We are primaraly interested in
constraining the halo mass range hosting detectable LAEs under the
conditions defined by \cite{Yamada2012}. In what follows will describe by
the letter ${\mathcal M}$ a model defined by an specific choice of the
three scalar parameters $M_{\rm min}$, $M_{\rm  max}$ y $f_{\rm occ}$.

For each model ${\mathcal M}$ we create a set of mock fields from
disjoint volumes in the simulation. Each volume has the same geometry
probed by Suprime-CAM and the narrow band filter, namely rectangular
cuboids of dimensions $46\times 35\times 41$ $h^{-3}$Mpc$^{3}$ where
the last dinemsion goes in the redshift direction. This corresponds to
a total area of $880$ arcmin$^{2}$ in each mock field. We construct a total
$5\times 7 \times 6=210$ of such volumes from a snapshot in the Bolshoi
simulation. In each mock field a LAE is assigned to the position of a
dark matter halo if the halo mass is in the range allowed by the model
$M_{\rm min}<M_{\rm h}<M_{\rm max}$ and a random variable taken from
an homogeneous distribution $0\leq \xi<1$ is smaller than the occupation
fraction $\xi<f_{\rm occ}$.

@@

\subsection{Sampling and Selecting Models}

We make a thorough exploration of the parameter space for the models
${\mathcal M}$. $\log_{10} M_{\rm min}$ takes $30$ values from $10.0$ up
to $12.9$ with an even spacing of $0.1$ dex. $\log_{10} M_{\rm max}$
takes values in the same range as $\log_{10}M_{\rm min}$ only with a
displacement of $0.1$ dex in the whole range. The occupation fraction
$f_{\rm occ}$ takes $10$ different values from $0.1$ to $1$ regulary
spaced by $0.1$. In total the number of different models ${\mathcal
  M}$ that are explored is $30 \times 30 \times 10 = 9000$.

For each mock survey generated in a given model ${\mathcal M}$ we
compute the surface density in the $12$ mock fields. We perform a
Kolmogorov-Smirnov (KS) to compare this mock date against the $12$
observational values. From this test we obtain a value $0<P<1$ to
reject the null hypotesis, namely that two data sets come from the
same distribution. In this paper we consider that for values $P>0.05$
the two distributions can be thought as coming from the same
distribution.

In this paper we consider that a model
${\mathcal M}$ that has at least one (1) mock survey (out of 15)
consistent with the observed distribution of LAE number densities has
viable parameters thatdeserve to be considered for further analysis.

%For each mock survey generated in a given model ${\mathcal M}$ we compute the LAE surface density
%distributions for the three different ways of grouping the mock
%fields, as described in the previous section. For each sub-volume we
%project the positions of the LAE hosting halos along the $z$ direction
%and calculate its surface number density in units of sources per
%arcmin$^{2}$. For each number density distribution we perform a
%Kolmogorov-Smirnov against the $12$ surface density observational
%values. From this test we obtain the value $0<P<1$ to reject the null
%hypothesis, namely that the two data sets come from the same
%distribution. In this paper we use values of $P>0.1$ to consider that
%the simulated and observed number densities come from the same
%distribution.

%We generate a series of models ${\mathcal M}$ with different input
%parameters$\{M_{\rm min}, M_{\rm max}, f_{\rm occ}\}$ as
%follows. $M_{\rm min}$ and $M_{\rm max}$ are allowed to take 30
%different values evenly spaced by $0.1$ dex, $M_{\rm min}$ ranges from
%$\log_{10}M_{\rm min}=10.0$ up to $\log_{10}M_{\rm min}=12.9$, while
%$M_{\rm max}$ range  from $\log_{10}M_{\rm min}=10.1$ up to
%$\log_{10}M_{\rm min}=13.0$. The occupation fraction $f_{\rm occ}$
%takes 100 different values from $0.01$ to $1.00$ regularly spaced by
%$0.01$. In total the number of different sets of input parameters to
%be explored is $30 \times 30\times 100 = 9\times 10^{4}$.

@@

\begin{figure}
\begin{center}
\includegraphics[width=1.10\linewidth,angle=0]{./plots/Fig1.pdf}
\caption{ \label{figure:laes_dist} Surface density of dark
  matter halos as a function of a minimum halo mass to count the
  total number of elements in a volume. Each line represents on of the
  $210$ volumes of dimensions $46\times 35\times 41$ h${-3}$Mpc$^{3}$
  in the Bolshoi simulation. The horizontal grey band represents the
  range of surface densities observed for LAEs at $z=3.1$ as reported
  by \citep{Yamada2012}.}
\end{center} 
\end{figure}

@@

\section{Additional Constraints}
